%-------------------------
% Resume in Latex
% Author : Nandini Mehrotra
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
 
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{setspace}
\usepackage{fontawesome}
\usepackage[dvipsnames]{xcolor}
\usepackage{xcolor}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}
\usepackage{courier}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%Line spacing
\renewcommand{\baselinestretch}{1.0}


%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\definecolor{light-gray}{gray}{0.95}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \vspace{-0.2cm}
    \textbf{\Huge \scshape Nandini Mehrotra} \\ \vspace{5pt}
    \small {\faPhone} 226-507-4163 \hspace{3pt}   \href{mailto:n3mehrot@uwaterloo.ca}{{\faEnvelope} n3mehrot@uwaterloo.ca} \hspace{3pt}  
    \href{https://www.linkedin.com/in/nandini-mehrotra-b179171b5/}{{\faLinkedinSquare} linkedin.com/in/nandinimehrotra} \hspace{3pt}
    \href{https://github.com/NandiniMeh}{{\faGithub} github.com/NandiniMeh}
\end{center}
\vspace*{-\baselineskip}

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: HTML/CSS, JavaScript, C/C++, R, Racket, Bash, Shell} \\
     \textbf{Frameworks \& Technologies}{: React, WordPress, Bootstrap, Figma} \\
     \textbf{Additional}{: Remote work with C++ on Linux OS (Ubuntu) using WSL, Bash Commands} \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Content Writer}{October 2020 - December 2020}
      {Platform Universal}{Remote: Dubai, UAE}
      \resumeItemListStart
        \resumeItem{Collaborated with 5-person team to deliver blog content (written and visual) for launch of website aimed at mental health awareness among university students.}
        \resumeItem{Coordinated with marketing and design teams to illustrate written content.}
        \resumeItem{Conducted keyword research and used SEO guidelines to optimize content.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {President Editorial Board}{April 2019 - April 2020}
      {Delhi Private School Sharjah}{Sharjah, UAE}
      \resumeItemListStart
        \resumeItem{Applied understanding of public opinion, social media, and traditional media use to create engaging content.}
        \resumeItem{Published and maintained collaborative ‘student blog’ network for 5700+ students to read and submit original written pieces.}
        \resumeItem{Cultivated knowledge of HTML/CSS through this project.}
    \resumeItemListEnd

    \resumeSubheading
      {Student Researcher and Product Designer}{April 2018 - February 2019}
      {Global Research and Immersion Programme (NUS and NTU Universities)}{Singapore}
      \resumeItemListStart
        \resumeItem{Led 8-month research and design thinking period on causes of traffic with 4-person team.}
        \resumeItem{Built virtual prototype of AI-driven dividers that divide road according to density of traffic as solution to identified problem using Figma.}
        \resumeItem{Pitched idea to NUS and NTU university professors in Singapore and Road and Transport Authority in Dubai, received recognition for innovative thinking and creative pitch deck.}
        \resumeItem{Complied a 65-page pitch deck and 2 progress reports on research, assessing progress in line with design thinking objectives.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS AND HACKATHONS-----------
\section{Projects and Hackathons}
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{SaveTwitter! {\href{https://github.com/NandiniMeh/save-twitter-game}{\faGithub}}} $|$ \emph{HTML5/CSS3, JavaScript}}{October 2021}
          \resumeItemListStart
            \resumeItem{Built a recreated version of the famous Dinosaur Game from Google Chrome Browser Offline}
            \resumeItem{Simple and easy-to-use GUI provided for better gameplay}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{Design Portfolio {\href{https://github.com/NandiniMeh/design_portfolio_iteration01}{\faGithub}}} $|$ \emph{HTML5/CSS3, Bootstrap} }{May 2021 -- Present}
          \resumeItemListStart
            \resumeItem{Developing second iteration of personal website showcasing design approach and prototypes for projects.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{CoviTrack}-TOHacks Submission {\href{https://github.com/NandiniMeh/CoviTrack}{\faGithub}} $|$ \emph{HTML5/CSS3, Figma, echoAR}}{May 2021}
          \resumeItemListStart
            \resumeItem{Ideated mobile and desktop platform as 2-person team for an all-in-one stop for healthy living during the pandemic}
            \resumeItem{Implemented vaccine appointment booking and daily health-check features.}
          \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{TheHub}-TILE Designathon Submission {\href{https://github.com/NandiniMeh/TheHub}{\faGithub}} $|$ \emph{Figma}}{March 2021}
          \resumeItemListStart
            \resumeItem{Ideated interactive mobile platform for isolated post-secondary students to enhance meaningful connections.}
            \resumeItem{Designed HiFis, LoFis, Branding and Prototype.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------VOLUNTEERING-----------
\section{Volunteering}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf {Orientation Director and Leader, University of Waterloo}}{May 2021 - September 2021}
      \resumeItemListStart
            \resumeItem{Acted as an upper-year mentor to 60 incoming first year students.}
          \resumeItemListEnd
    \resumeProjectHeading
      {\textbf {Brand Ambassador, Protect Your Mom Awareness Campaign}}{September 2019 - Present}
      \resumeItemListStart
            \resumeItem{Led team of 15 coordinators in conducting campaigns about breast cancer for an audience of over 200 students.}
          \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, ON, Canada}
      {Bachelor of Science in Computer Science}{Expected Graduation: 2025}
      \resumeItemListStart
            \resumeItem{\textbf {Awards}: President’s Scholarship of Distinction}
          \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
